alluvial diagrams in ggplot2

### 2017-11-05 inst/doc/ggalluvial.rmd
debug 'aggregate.wts' + default FALSE

```{r example alluvial diagram using Titanic dataset, echo=FALSE}
ggplot(data = to_lodes(as.data.frame(Titanic),
                       key = "Demographic",
                       axes = 1:3),
       aes(x = Demographic, stratum = value, alluvium = id,
           weight = Freq, label = value)) +
  geom_alluvium(aes(fill = Survived)) +
  geom_stratum() + geom_text(stat = "stratum") +
  ggtitle("passengers on the maiden voyage of the Titanic",
          "stratified by demographics and survival")
```

@@

```{r Berkeley admissions dataset}
head(as.data.frame(UCBAdmissions), n = 12)
is_alluvial(as.data.frame(UCBAdmissions), logical = FALSE)
```

@@

```{r lode form of Berkeley admissions dataset}
UCB_lodes <- to_lodes(as.data.frame(UCBAdmissions), axes = 1:3)
head(UCB_lodes, n = 12)
is_alluvial(UCB_lodes, logical = FALSE)
```

@@

```{r alluvial diagram of majors dataset}
data(majors)
majors$curriculum <- as.factor(majors$curriculum)
ggplot(majors,
       aes(x = semester, stratum = curriculum, alluvium = student,
           fill = curriculum, label = curriculum)) +
  geom_flow(stat = "alluvium", lode.guidance = "rightleft") +
  geom_stratum() +
  theme(legend.position = "bottom") +
  ggtitle("student curricula across several semesters")
```

>>>>

```{r example alluvial diagram using Titanic dataset, echo=FALSE}
ggplot(data = to_lodes(as.data.frame(Titanic),
                       key = "Demographic",
                       axes = 1:3),
       aes(x = Demographic, stratum = stratum, alluvium = alluvium,
           weight = Freq, label = stratum)) +
  geom_alluvium(aes(fill = Survived)) +
  geom_stratum() + geom_text(stat = "stratum") +
  ggtitle("passengers on the maiden voyage of the Titanic",
          "stratified by demographics and survival")
```

@@

```{r Berkeley admissions dataset}
head(as.data.frame(UCBAdmissions), n = 12)
is_alluvial(as.data.frame(UCBAdmissions), logical = FALSE, silent = TRUE)
```

@@

```{r lode form of Berkeley admissions dataset}
UCB_lodes <- to_lodes(as.data.frame(UCBAdmissions), axes = 1:3)
head(UCB_lodes, n = 12)
is_alluvial(UCB_lodes, logical = FALSE, silent = TRUE)
```

@@

```{r alluvial diagram of majors dataset}
data(majors)
majors$curriculum <- as.factor(majors$curriculum)
ggplot(majors,
       aes(x = semester, stratum = curriculum, alluvium = student,
           fill = curriculum, label = curriculum)) +
  geom_flow(stat = "alluvium", lode.guidance = "rightleft",
            color = "black") +
  geom_stratum() +
  theme(legend.position = "bottom") +
  ggtitle("student curricula across several semesters")
```
